---
title: "Clustering"
author: "SP"
date: "July 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercises 0 and 1 Clustering
INstalling packages and removing column type using scale function. WOrking on first method of clustering

```{r Clustering}
# Exercise 0: Install these packages if you don't have them already
#install.packages(c("cluster", "rattle","NbClust"))
#install.packages("flexclust")
# loading the data and looking at the first few rows
data(wine, package="rattle")
head(wine)

# Exercise 1: Remove the first column from the data and scale
wine <- scale(wine[-1]) 


# Cluster the data using K-Means.
# 1st Method

wssplot <- function(data, nc=15, seed=1234){
	              wss <- (nrow(data)-1)*sum(apply(data,2,var))
               	      for (i in 2:nc){
		        set.seed(seed)
	                wss[i] <- sum(kmeans(data, centers=i)$withinss)}
	                
		      plot(1:nc, wss, type="b", xlab="Number of Clusters",
	                        ylab="Within groups sum of squares")
	   }

wssplot(wine)
``` 
Since there is distinct drop within sum of squares between 1 and 3 clusters, we can set for 3 clusters solution. 


## Exercises 2 and 3
 Use the NbClust library, which runs many experiments and gives a distribution of potential number of clusters.
``` {r}
library(NbClust)
wssplot(df)                                      
set.seed(1234)
nc <- NbClust(df, min.nc=2, max.nc=15, method="kmeans")
table(nc$Best.n[1,])
```


## Exercise 4
Running the Kmean cluster 
```{r}
# Use the Kmean method 
set.seed(1234)
fit.km <- kmeans(df, 3, nstart=25)
fit.km$size
fit.km$centers   
```

## Exercise 5 andd 6
Performing cross-tabulation of cluster and type using table(). Using Rnak index i am quanitifying agreement between type and cluster

```{r}
data(wine, package="rattle")
ct.km <- table(wine$Type, fit.km$cluster)
ct.km

library(flexclust)
randIndex(ct.km)

```
Rand index is 0.9 which si pretty solid cluster solution. 
